Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-08-05 Paper/method.tex
sec 3, edits and comments ...

In this section, we present the computational strategy used for computing the
active subspace in the case of H$_2$/O$_2$ reaction kinetics with uncertain
pre-exponent of individual reaction rates provided in Table~\ref{tab:kinetics}.
Specifically, we employ two strategies: 
A gradient-based strategy that involves computation of model
gradients in order to construct the matrix $\hat{\mat{C}}$
in~\eqref{eq:chat}, and a gradient-free approach 
that involves a (\alennote{should we say 
regression-based?}) local linear approximation of
the model output to circumvent the computational cost associated with gradient
computation. The gradient-based approach is based on Algorithm
1.1, and the gradient-free approach is based on Algorithm 1.2
in~\cite{Constantine:2015}. In this work, we implement the two
strategies in an iterative manner and demonstrate potential for
additional savings in both cases.  For the present application,
our findings based on the two strategies are observed to be consistent.  
Since,
the gradient-free approach is more efficient, this observation
encourages its use for high-dimensional applications as discussed later in
Section~\ref{sec:app}. 
%Note however, that the model output is required to be
%differentiable throughout the input domain in both cases.

@@

\alennote{I don't see the point of this paragraph; part of it that 
explains the gradient-free approach is unclear, and the part 
that seems to motivate its use is something to mention in the introduction.
Just say what the gradient-free approach is about, and say that we 
follow an iterative strategies as before.}
As mentioned earlier, the gradient-free approach does not involve computation
of the gradient of the model output. Instead, a least-squares fit is performed
to the local linear regression-based approximation to the model output. While
the gradient-free approach offers a significant potential for additional
computational savings, its ability to reasonably approximate the active
subspace has not been investigated for a wide variety of
problems~\cite{Constantine:2015}. We are motivated by the
potential of this approach in reducing the computational effort
associated with the active subspace computation. Moreover, this effort could
help advance this approach and further motivate its usage for a wide variety of
high-dimensional applications in the future.

>>>>

In this section, we present the computational strategy used for computing the
active subspace in the case of H$_2$/O$_2$ reaction kinetics with uncertain
pre-exponent of individual reaction rates provided in Table~\ref{tab:kinetics}.
Specifically, we employ two strategies: 
A gradient-based strategy that involves computation of model
gradients in order to construct the matrix $\hat{\mat{C}}$
in~\eqref{eq:chat}, and a gradient-free approach 
that involves a 
local linear approximation of
the model output to circumvent the computational cost associated with gradient
computation. 
(\alennote{should we say regression-based local linear approximation? 
When I hear local linear approximation I think of Taylor expansion, and
probably many readers will do the same; so saying gradient-free
local linear approximation might be confusing to some people.}) 
The gradient-based approach is based on Algorithm
1.1, and the gradient-free approach is based on Algorithm 1.2
in~\cite{Constantine:2015}. In this work, we implement the two
strategies in an iterative manner and demonstrate potential for
additional savings in both cases.  For the present application,
our findings based on the two strategies are observed to be consistent.  
Since,
the gradient-free approach is more efficient, this observation
encourages its use for high-dimensional applications as discussed later in
Section~\ref{sec:app}. 
%Note however, that the model output is required to be
%differentiable throughout the input domain in both cases.

@@

\alennote{I don't see the point of this paragraph; part of it that 
explains the gradient-free approach is unclear, and the part 
that seems to motivate its use is something to mention in the introduction.
Just say what the gradient-free approach is about, and say that we 
follow an iterative strategies as before.}
As mentioned earlier, the gradient-free approach does not involve computation
of the gradient of the model output. Instead, a least-squares fit is performed
to the local linear regression-based approximation to the model output. While
the gradient-free approach offers a significant potential for additional
computational savings, its ability to reasonably approximate the active
subspace has not been investigated for a wide variety of
problems~\cite{Constantine:2015}.~\alennote{I would not say this. 
If Paul (or a student of his) 
reviews this article, he will probably disagree. Remember that 
book was from several years ago. Instead, say that we 
demonstrate its utility for efficient response surface construction in 
chemical kinetics modeling.} We are motivated by the
potential of this approach in reducing the computational effort
associated with the active subspace computation. Moreover, this effort could
help advance this approach and further motivate its usage for a wide variety of
high-dimensional applications in the future.
